Characterizing edges in signed and vector-valued graphs

### 2017-12-13 cc/gtx_experiments.tex
fix cc chapter layout

The three kinds of topology we consider are:
\begin{description}[leftmargin=*]
	\item[\grid{}] which are 2D lattices, where each node has four neighbors except on the boundary.
		The synthetic ones are square, while the \enquote{real world} ones represents the four neighbors
		pixel connectivity of the pictures showed in \autoref{fig:gtx_xp_bwpics}.
	\item[\lpa{}] which are built synthetically according to the model of \textcite{Barabasi1999}.
		While this does not follow the more rigorous specification of \textcite{PAmodel04}, informally,
		we start with a line graph of $m$ nodes and add node one by one until the graph consists of $n$
		nodes. Each time a new node is added, it is connected to $m$ of the existing nodes with a
		probability proportional to their degree. Here we choose $m=3.13$, that is when adding a new
		node, we pick $3$ or $4$ existing neighbors such the initial expected number of neighbors for
		each new nodes is $3.13$. Such graphs are quite sparse and have short diameter, thus providing a
		crude but reasonable approximation of online social networks. Therefore, the real world
		instances of the \lpa{} model are \wik{}, \sla{} and \epi{} networks from \autoref{chap:troll}
		 along with \gplus{}. The last one is constructed from
		ego networks of \gplus{}\footnote{Available at
		\url{http://snap.stanford.edu/data/egonets-Gplus.html}} by keeping the largest connected
		component of users whose gender is known. Basic statistics of those real \lpa{} graphs are
		presented in (\autoref{tab:gtx_xp_dataset}). 
	\item[\triangle{}] which consists of a Delaunay triangulation of a set of points randomly
		located in a 2D space.\footnote{As
		implemented by the \textsf{graph-tool} library (\url{https://graph-tool.skewed.de})}
\end{description}

@@

On \lpa{} and \triangle{}, we see in \autoref{fig:gtx_xp_st} that both trees exhibits logarithmic stretch, although with a
larger constant for \gtx{}. Note that this is also the case for others low stretch tree methods
\autocite[Section 5.3.1]{papplow}. On \grid{} however, \gtx{} preserves this logarithmic stretch growth
while this is visually no longer the case for \bfs{}.
In that case, we cannot expect a better stretch than $\frac{\log n}{2048}$ according to
\autocite[Theorem 6.6]{LowerBound95}.

@@

Like in \autoref{s:exp}, we evaluate the performance of our prediction using the Matthews
Correlation Coefficient (MCC), defined in equation~\autoref{eq:troll_mcc} \vpageref{eq:troll_mcc}.
As showed in \autoref{fig:gtx_xp_mcc}, when the noise level is low, \gtx{} performs better than
\bfs{}. As the noise level gets higher, they have similar performance. Note also than in
\autoref{fig:gtx_xp_pasynthmcc}, \gtx{} is less sensible to the size of the graph.

@@

As the \asym{} has a $O(n^3)$ complexity and uses quite some memory at prediction time, the larger
graphs used previously are not all included. The conclusion of \autoref{fig:gtx_xp_asym} is that
except on social networks, it is better to use spanning trees than random edges. Specifically, \gtx{}
on \grid{} and \bfs{} elsewhere.

\begin{figure}[tbh]
	\centering
	\begin{subfigure}[b]{0.47\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/grsynthasym}
		\caption{Synthetic \grid{} \label{fig:gtx_xp_grsynthasym}}
	\end{subfigure}~
	\begin{subfigure}[b]{0.47\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/grrwasym}
		\caption{\enquote{Real} \grid{} }\label{fig:gtx_xp_grrwasym}
	\end{subfigure}
	\begin{subfigure}[b]{0.47\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/pasynthasym}
		\caption{Synthetic \lpa{} }\label{fig:gtx_xp_pasynthasym}
	\end{subfigure}~
	\begin{subfigure}[b]{0.47\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/trasym}
		\caption{\triangle{} }\label{fig:gtx_xp_trasym}
	\end{subfigure}
	\begin{subfigure}[b]{0.47\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/parwasym}
		\caption{Real world network }\label{fig:gtx_xp_parwasym}
	\end{subfigure}
	\caption{\asym{} over various graphs}\label{fig:gtx_xp_asym}
\end{figure}

>>>>

The three kinds of topology we consider are:
\begin{description}[leftmargin=*]
	\item[\grid{}] which are 2D lattices, where each node has four neighbors except on the boundary.
		The synthetic ones are square, while the \enquote{real world} ones represents the four neighbors
		pixel connectivity of the pictures showed in \autoref{fig:gtx_xp_bwpics}
		\vpageref{fig:gtx_xp_bwpics}.
	\item[\lpa{}] which are built synthetically according to the model of \textcite{Barabasi1999}.
		While this does not follow the more rigorous specification of \textcite{PAmodel04}, informally,
		we start with a line graph of $m$ nodes and add node one by one until the graph consists of $n$
		nodes. Each time a new node is added, it is connected to $m$ of the existing nodes with a
		probability proportional to their degree. Here we choose $m=3.13$, that is when adding a new
		node, we pick $3$ or $4$ existing neighbors such the initial expected number of neighbors for
		each new nodes is $3.13$. Such graphs are quite sparse and have short diameter, thus providing a
		crude but reasonable approximation of online social networks. Therefore, the real world
		instances of the \lpa{} model are \wik{}, \sla{} and \epi{} networks from \autoref{chap:troll}
		 along with \gplus{}. The last one is constructed from
		ego networks of \gplus{}\footnote{Available at
		\url{http://snap.stanford.edu/data/egonets-Gplus.html}} by keeping the largest connected
		component of users whose gender is known. Basic statistics of those real \lpa{} graphs are
		presented in (\autoref{tab:gtx_xp_dataset}). 
	\item[\triangle{}] which consists of a Delaunay triangulation of a set of points randomly
		located in a 2D space.\footnote{As
		implemented by the \textsf{graph-tool} library (\url{https://graph-tool.skewed.de})}
\end{description}

@@

On \lpa{} and \triangle{}, we see in \autoref{fig:gtx_xp_st} \vpageref{fig:gtx_xp_st} that both trees exhibits logarithmic stretch, although with a
larger constant for \gtx{}. Note that this is also the case for others low stretch tree methods
\autocite[Section 5.3.1]{papplow}. On \grid{} however, \gtx{} preserves this logarithmic stretch growth
while this is visually no longer the case for \bfs{}.
In that case, we cannot expect a better stretch than $\frac{\log n}{2048}$ according to
\autocite[Theorem 6.6]{LowerBound95}.

@@

Like in \autoref{s:exp}, we evaluate the performance of our prediction using the Matthews
Correlation Coefficient (MCC), defined in equation~\autoref{eq:troll_mcc} \vpageref{eq:troll_mcc}.
As showed in \autoref{fig:gtx_xp_mcc} \vpageref{fig:gtx_xp_mcc}, when the noise level is low, \gtx{} performs better than
\bfs{}. As the noise level gets higher, they have similar performance. Note also than in
\autoref{fig:gtx_xp_pasynthmcc}, \gtx{} is less sensible to the size of the graph.

@@

As the \asym{} has a $O(n^3)$ complexity and uses quite some memory at prediction time, the larger
graphs used previously are not all included. The conclusion of \autoref{fig:gtx_xp_asym} \vpageref{fig:gtx_xp_asym} is that
except on social networks, it is better to use spanning trees than random edges. Specifically, \gtx{}
on \grid{} and \bfs{} elsewhere.

\begin{figure}[tbh]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/grsynthasym}
		\caption{Synthetic \grid{} \label{fig:gtx_xp_grsynthasym}}
	\end{subfigure}~
	\begin{subfigure}[b]{0.475\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/grrwasym}
		\caption{\enquote{Real} \grid{} }\label{fig:gtx_xp_grrwasym}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/pasynthasym}
		\caption{Synthetic \lpa{} }\label{fig:gtx_xp_pasynthasym}
	\end{subfigure}~
	\begin{subfigure}[b]{0.475\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/trasym}
		\caption{\triangle{} }\label{fig:gtx_xp_trasym}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\includegraphics[width=\textwidth]{gtx_exp/parwasym}
		\caption{Real world network }\label{fig:gtx_xp_parwasym}
	\end{subfigure}
	\caption{\asym{} over various graphs}\label{fig:gtx_xp_asym}
\end{figure}
